---
title: "Lab 00 - Hello IDS!"
author: "GRACE TAIT"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Khushi", "Danish", "Moses", 
           "Andrew", "Divyam"),
  github_username = c("khushiwadhwa0210", "NDRaziq", "Mosesweintraub", 
                      "andrewrightjames", "DivyamAneja"), 
  colour = c("red", "green", "red", 
             "blue", "blue"),
  hobby = c("annoyingpeople", "music", "rowing", 
            "rowing", "cricket"),
  favourite_number = c(2, 7, 9, 2, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data.

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```

It shows a bar chart for which number and colour each team member likes.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Team Member's Username", 
          y = "Team Member's Favourite Number",
          title = "Team Member's Data")
```

I think that it changes the titles of the axis.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It would not be good at conveying information because the majority of people would have unique hobbies so there would be 100+ bars. A better way of displaying data would be to group hobbies together. 
